Visuals

### 2024-11-07 scripts/visuals.Rmd
revision

```{r setup, include=FALSE}
library(tidyverse)
library(jsonlite)
library(stringr)
library(ggpubr)
library(tidyboot)
library(readxl)
library(brms)
library(ggthemes)
library(writexl)
library(ggdist)
library(sf)
library(geomtextpath)
library(ggridges)
```

```{r}
data <- read_csv("../data/previc_data.csv")%>%
  mutate(age_group = factor(substr(age, 1,1)))
```

@@

```{r}
wac <- data%>%
  group_by(subjID)%>%
  mutate(n = n())%>%
  filter(n == 379)%>%
  select(-n)%>%
  group_by(word, aoa_rating_german, word_type)%>%
  summarise(mean = mean(score))%>%
  ggplot(aes(x = aoa_rating_german, y = mean, col = word_type, fill = word_type))+
  geom_smooth( method = "lm", alpha = .2)+
  ylim(0,1)+
  labs(x = "Rated age of acquisition", y = "Proportion response yes")+
  geom_point(pch = 1, alpha = 0.5)+
  stat_cor(label.y.npc = "bottom", show.legend = FALSE, aes(label = paste(..r.label..)), cor.coef.name = "r")+
  scale_color_colorblind(name = "Word type", guide = "none")+
  scale_fill_colorblind(name = "Word type", guide = "none")+
  #facet_grid(~word_type)+
  theme_few()
```

```{r}
pac<- data%>%
  group_by(subjID)%>%
  mutate(n = n())%>%
  filter(n == 379)%>%
  select(-n)%>%
  group_by(subjID, age, word_type)%>%
  #group_by(subjID, age)%>%
  summarise(mean = mean(score))%>%
  ggplot(aes(x = age, y = mean, col = word_type))+
  labs(x = "Child age", y = "Proportion response yes")+
  geom_point(pch = 1, alpha = 0.5)+
  geom_smooth(method = "lm")+
  stat_cor(label.y.npc = "bottom",label.x.npc = 0.8, show.legend = FALSE, aes(label = paste(..r.label..)), cor.coef.name = "r")+
  scale_color_colorblind(name = "Word type", guide = guide_legend(reverse = TRUE))+
  scale_fill_colorblind(name = "Word type", guide = guide_legend(reverse = TRUE))+
  #facet_grid(~word_type)+
  theme_bw()
```
```{r}
ggarrange(wtd, wac,pac, nrow = 1, labels = c("A","B", "C"), widths = c(0.7,1,1.2))
```
```{r}
ggsave("../graphs/fig2.png", width = 12, height = 3, scale = 1.25, bg = "white")
```

@@

link_data <- data%>%
  filter(word %in% final_items)%>%
  group_by(subjID)%>%
  summarise(previc = sum(score))%>%
  left_join(orev_data%>%
              group_by(subjID)%>%
              summarise(orev = sum(correct)))%>%
  filter(!is.na(orev))%>%
   ungroup()%>%
  distinct(subjID, .keep_all = T)
```

@@

@@

```{r}
plot_grid(p_iitic, 
          plot_grid(pcpo,pme, align = 'v', ncol = 1, labels = c("B","C")),
          labels = c("A",""), rel_widths = c(3,1))
```

```{r}
ggsave("../graphs/fig4.png", height = 4, width = 10, scale = 1.25, bg = "white")
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(jsonlite)
library(stringr)
library(ggpubr)
library(tidyboot)
library(readxl)
library(brms)
library(ggthemes)
library(writexl)
library(ggdist)
library(sf)
library(grid)
library(geomtextpath)
library(ggridges)
```

```{r}
data <- read_csv("../data/previc_data.csv")%>%
  mutate(age_group = factor(substr(age, 1,1)))
```
## Figure Rasch

```{r}
icc <- readRDS("../saves/icc1_final.rds")%>%
  filter(item == "Kunde")

p_rasch <- icc %>% 
  left_join(data%>%distinct(word, word_type)%>%rename(item = word))%>%
  ggplot(aes(x = theta, y = p,group = item)) +
  geom_hline(yintercept = 0.5, lty = 3, alpha = 0.5)+
  geom_line() +
  scale_y_continuous(breaks = c(0,0.5, 1))+
  labs(x = "Latent ability (expressive language)",
       y = "Probability to answer 'yes'") +
  theme_few()+
  theme(legend.position = c(0.85, 0.2), legend.direction = "vertical", legend.title.align = 0.5, legend.background = element_blank())
```
```{r}
ggsave("../graphs/figr.png", width = 4, height = 3, scale = 1, bg = "white")
```

@@

```{r}
wac <- data%>%
  group_by(subjID)%>%
  mutate(n = n())%>%
  filter(n == 379)%>%
  select(-n)%>%
  group_by(word, aoa_rating_german, word_type)%>%
  summarise(mean = mean(score))%>%
  ggplot(aes(x = aoa_rating_german, y = mean, col = word_type, fill = word_type))+
  geom_smooth(method = "loess", alpha = .2)+
  #geom_smooth( method = "lm", alpha = .2)+
  ylim(0,1)+
  labs(x = "Rated age of acquisition", y = "Proportion response yes")+
  geom_point(pch = 1, alpha = 0.5)+
  #stat_cor(label.y.npc = "bottom", show.legend = FALSE, aes(label = paste(..r.label..)), cor.coef.name = "r")+
  scale_color_colorblind(name = "Word type", guide = "none")+
  scale_fill_colorblind(name = "Word type", guide = "none")+
  #facet_grid(~word_type)+
  theme_few()
```

```{r}
pac<- data%>%
  group_by(subjID)%>%
  mutate(n = n())%>%
  filter(n == 379)%>%
  select(-n)%>%
  group_by(subjID, age, word_type)%>%
  #group_by(subjID, age)%>%
  summarise(mean = mean(score))%>%
  ggplot(aes(x = age, y = mean, col = word_type))+
  labs(x = "Child age", y = "Proportion response yes")+
  geom_point(pch = 1, alpha = 0.5)+
  geom_smooth(method = "loess", alpha = .2)+
  #stat_cor(label.y.npc = "bottom",label.x.npc = 0.8, show.legend = FALSE, aes(label = paste(..r.label..)), cor.coef.name = "r")+
  scale_color_colorblind(name = "Word type", guide = guide_legend(reverse = TRUE))+
  scale_fill_colorblind(name = "Word type", guide = guide_legend(reverse = TRUE))+
  #facet_grid(~word_type)+
  theme_bw()
```
```{r}
ggarrange(wtd, wac,pac, nrow = 1, labels = c("A","B", "C"), widths = c(0.7,1,1.2))
```
```{r}
ggsave("../graphs/fig2.png", width = 12, height = 3, scale = 1.25, bg = "white")
```

@@

link_data <- data%>%
  filter(word %in% readRDS("../saves/final_items.rds"))%>%
  group_by(subjID)%>%
  summarise(previc = sum(score))%>%
  left_join(orev_data%>%
              group_by(subjID)%>%
              summarise(orev = sum(correct)))%>%
  filter(!is.na(orev))%>%
   ungroup()%>%
  distinct(subjID, .keep_all = T)
```

@@

```{r}
awstr_data <- read_csv("../data/previc_validation.csv")

pcpa <- ggplot(awstr_data, aes(y = previc, x = awst_r_score))+
  geom_jitter(pch = 1,  alpha = .5, size = 1, height = 0, width = 0.1)+
  stat_cor(show.legend = FALSE, aes(y = previc, x = awst_r_score, label = paste(..r.label..)),inherit.aes = F, cor.coef.name = "r")+
  geom_smooth(method = "lm", inherit.aes = F, aes(y = previc, x = awst_r_score), col = "firebrick")+
  labs(y = "PREVIC score", x = "AWST-R score")+
  theme_few()
```

@@

```{r}
plot_grid(p_iitic, 
          plot_grid(pcpo,pcpa, align = 'hv', ncol = 1, labels = c("B","C")),
          labels = c("A",""), rel_widths = c(3,1))
```

```{r}
ggsave("../graphs/fig4.png", height = 5, width = 10, scale = 1.25, bg = "white")
```
